On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2025-03-01 char-4k-bound/char-4k-bound.tex
[4k3] Verify the case p<10 explicitly - fix the Referee's comment
[4k3] Refactor Corollary 5.5. a bit - fix the Referee's comment

\begin{corollary}
	\label{cor:sqrt_5_3}
	For the height of a triangle $ABC$, where ${A, B, C} \subset M \in \overline{\mathfrak{M}_4}'$, with sides $3 \leq a \leq b \leq c$, the following estimate holds:
	$$
		(2a-1)^{1/2} \geq \frac{\sqrt{5}}{\sqrt{3}} a^{1/2},
	$$
	where the difference between the left and right-hand sides increases with increasing $a$.
\end{corollary}

@@

	Now we have to consider $m > \frac{6}{5}p^{2/5}$.
	Then for any points $A, B \in M \setminus {M_1}$, we have $|AB| > \frac{6}{5}p^{2/5}$.
	By Corollary~\ref{cor:sqrt_5_3} and Lemma~\ref{lem:smurov_min_height},
	no three points from $M \setminus {M_1}$ lie in a strip of width
	\begin{equation}
		\frac{\sqrt{5}}{\sqrt{3}} \cdot \sqrt{\frac{6p^{2/5}}{5}} = \sqrt{2} \cdot p^{1/5}
		.
	\end{equation}

>>>>

\begin{corollary}
	\label{cor:sqrt_5_3}
	In a triangle $ABC$ with sides $3 \leq a \leq b \leq c$, where ${A, B, C} \subset M \in \overline{\mathfrak{M}_4}'$, the smallest height is at least $(2a-1)^{1/2}$.
\end{corollary}

\begin{proof}
	Indeed, for $a\geq 3$ the inequality
	$$
		(2a-1)^{1/2} \geq \frac{\sqrt{5}}{\sqrt{3}} a^{1/2}
	$$
	holds, and
	the difference between the left and right-hand sides increases with increasing $a$.
\end{proof}

@@

	If $n\geq 4$ and $p < 10$, then the claim of the theorem follows immediately from~\eqref{d}.
	So now we have to consider $m > \frac{6}{5}p^{2/5} > 3$.
	Then for any points $A, B \in M \setminus {M_1}$, we have $|AB| > \frac{6}{5}p^{2/5}$.
	By Corollary~\ref{cor:sqrt_5_3} and Lemma~\ref{lem:smurov_min_height},
	no three points from $M \setminus {M_1}$ lie in a strip of width
	\begin{equation}
		\frac{\sqrt{5}}{\sqrt{3}} \cdot \sqrt{\frac{6p^{2/5}}{5}} = \sqrt{2} \cdot p^{1/5}
		.
	\end{equation}
